---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##2

###(a)

```{r}
sales <- read.csv('/Users/chuanxu/Desktop/sales.csv', header = T) #read the data into R
sales <- ts(sales, start = 1999, frequency = 12) #format as a time series object

t <- time(sales) #extracting time
t2 <- t^2
#fit a "trend only" model where the trend component is quadratic in time
reg0 <- lm(sales~t+t2)
plot(sales)
points(t,predict.lm(reg0),type='l',col='red')

par(mfrow=c(2,2)) #Dividing the plotting page into 4 panels
plot(reg0$fitted, reg0$residuals, main = "Residuals vs. Fitted Values", 
     ylab = "Residuals", xlab = "Fitted Values") #plot of fitted values vs residuals
abline(h = 0, col = "red", lwd = 2)
qqnorm(reg0$residuals) #qq-plot of residuals
#plotting the line, along which the dots in qq-plot should lie
qqline(reg0$residuals, col = "red") 
#plotting the residuals vs time
plot(reg0$residuals, main = "Residuals vs. Time", ylab = "Residuals", xlab = "Time")
abline(h = 0, col = "red", lwd = 2) #plotting a horizontal line at 0
acf(reg0$residuals, main = "ACF Plot of Residuals") #sample acf plot of residuals
```

From the residuals vs. fitted values plot, we notice that the residuals "bounce randomly" and roughly form a "horizontal band" around the 0 line. This suggests that it's reasonable to assume the relationship is linear and the variances of the error terms are equal.

The Q-Q plot shows that residual quantiles match with the theoretical normal quantiles, suggesting that the normality assumption is reasonable.

From the residuals vs. time plot, we notice that there is "serial correlation" among the error terms, suggesting the assumption of independent error terms is violated.

The ACF plot indicates there is "seasonality" among the error terms.

###(b)

```{r}
month <- as.factor(cycle(sales)) #add a seasonal component to the model

reg1 <- lm(sales~t+t2+month)
plot(sales)
points(t,predict.lm(reg1),type='l',col='red')

par(mfrow=c(2,2)) #Dividing the plotting page into 4 panels
plot(reg1$fitted, reg1$residuals, main = "Residuals vs. Fitted Values", 
     ylab = "Residuals", xlab = "Fitted Values") #plot of fitted values vs residuals
abline(h = 0, col = "red", lwd = 2)
qqnorm(reg1$residuals) #qq-plot of residuals
#plotting the line, along which the dots in qq-plot should lie
qqline(reg1$residuals, col = "red") 
#plotting the residuals vs time
plot(reg1$residuals, main = "Residuals vs. Time", ylab = "Residuals", xlab = "Time")
abline(h = 0, col = "red", lwd = 2) #plotting a horizontal line at 0
acf(reg1$residuals, main = "ACF Plot of Residuals") #sample acf plot of residuals
```

From the residuals vs. fitted values plot, we notice that the residuals "bounce randomly" and roughly form a "horizontal band" around the 0 line. This suggests that it's reasonable to assume the relationship is linear and the variances of the error terms are equal.

The Q-Q plot shows that residual quantiles match closely with the theoretical normal quantiles, suggesting that the normality assumption is reasonable.

From the residuals vs. time plot, we notice that there is "serial correlation" among the error terms, suggesting the assumption of independent error terms is violated.

The ACF plot implies there is autoressive process of order 3.

###(c)

The ACF plot of the model in (a) indicates there is "seasonality" among the error terms. The ACF plot of the model in (b) implies the series is stationary and there is autoressive process of order 3.

###(d)

None of the two models above satisfies the fundamental assumptions of least square regression since the error term is not independent.

###(e)

```{r}
#Prediction in sales data
t.new <- seq(2011,2014,length=36)[1:36] # Intoducing new time for forecatsting 3 years 
t2.new <- t.new^2
month.new <- factor(rep(1:12,3)) # Introducing the seasonal value for forecasting

#Putting the values for forecasting into a dataframe
new <- data.frame(t=t.new, t2=t2.new, month=month.new) 
#Computing the prediction as well as prediction interval
pred <- predict.lm(reg1,new,interval='prediction') 

par(mfrow=c(1,1))
plot(sales,xlim=c(1999,2014),ylim=c(0,90)) #plotting the data

#adding a vertical line at the point where prediction starts
abline(v=2011,col='blue',lty=2) 
lines(pred[,1]~t.new,type='l',col='red') #plotting the predict
lines(pred[,2]~t.new,col='green') #plotting lower limit of the prediction interval
lines(pred[,3]~t.new,col='blue') #plotting upper limit of the  prediction interval
legend(2000, 80, legend = c('predict', 'lower limit', 'upper limit'), 
       col = c('red', 'green', 'blue'), lty = c(1,1,1))
```

###(f)

Hypothese tests, confidence intervals and prediction intervals would no longer be valid.