---
title: "Addtional Problem"
output: pdf_document
---

```{r setup, include=FALSE}
library(forecast)
library(tseries)
library(lmtest)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

##(a)

```{r}
adf.test(LakeHuron)
L1 <- diff(LakeHuron)
adf.test(L1)
```

Because now p-value is smaller than 0.01, the time series is stationary after differencing once.

##(b)

```{r}
m1 <- arima(x = LakeHuron, order = c(1,1,0), method = "ML")
m1
```

##(c)

```{r}
m2 <- arima(x = LakeHuron, order = c(2,1,0), method = "ML")
m2
```

##(d)

```{r}
#likelihood ratio test
lrtest(m1,m2)
```

Because it is significant, the null hypothesis is rejected. We believe AR(2) model is better than AR(1) model.

##(e)

Because in (d) the null hypothesis is rejected and the AIC and $\hat{\sigma}^2$ of AR(2) model are smaller than AR(1) model, AR(2) model will be "optimal".

##(f)

###i.

```{r}
#t-test for the residual to decide whether the mean of epsilons is 0
t.test(m2$residuals)
```

Because p-value is 0.9968, we can not reject the null hypothesis. We believe the mean of error terms is 0.

###ii.

```{r}
#scatterplot of residuals vs t
plot(m2$residuals, type = 'p')
abline(h = 0, col = 'red')
abline(h = mean(m2$residuals))
```

From the plot, we can see that the residuals roughly form a "horizontal band" around the 0 line and the mean of the residuals is close to 0. This suggests that the mean of error terms is 0 and the variances of the error terms are equal.

```{r}
#test for homoscedasticity
group1 <- data.frame(m2$residuals, groups = gl(2,49,98))
bartlett.test(m2$residuals~groups, data = group1)
group2 <- data.frame(m2$residuals, groups = gl(3,33,98))
bartlett.test(m2$residuals~groups, data = group2)
group3 <- data.frame(m2$residuals, groups = gl(4,25,98))
bartlett.test(m2$residuals~groups, data = group3)
group4 <- data.frame(m2$residuals, groups = gl(5,20,98))
bartlett.test(m2$residuals~groups, data = group4)
group5 <- data.frame(m2$residuals, groups = gl(6,17,98))
bartlett.test(m2$residuals~groups, data = group5)
group6 <- data.frame(m2$residuals, groups = gl(7,14,98))
bartlett.test(m2$residuals~groups, data = group6)
```

Because only the p-value when we have two groups is about 0.02, other p-values are all greater than 0.1, we believe there is no heteroscedasticity.

###iii.

```{r}
#ACF plot of residuals
acf(m2$residuals)
```

From the plot, we can see that there is no significant correlation between residuals.

```{r}
Box.test(m2$residuals, lag = 1, type = "Ljung")
Box.test(m2$residuals, lag = 5, type = "Ljung")
Box.test(m2$residuals, lag = 10, type = "Ljung")
Box.test(m2$residuals, lag = 20, type = "Ljung")
```

Because the p-value is greater than 0.5, we can not reject the null hypothesis. We believe there is no correlation between error terms.

###iv.

```{r}
#QQ-plot of residuals
qqnorm(m2$residuals)
qqline(m2$residuals)
```

From the plot, we can see the distribution of the residuals is close to the normal distribution.

```{r}
#normality test
normvec <- rnorm(length(m2$residuals))
ks.test(m2$residuals, normvec)
```

Because the p-value is greater than 0.1, we can not reject the null hypothesis. We believe the normal distribution assumption is met.

##(g)

```{r}
m2_fit <- LakeHuron - m2$residuals
plot(LakeHuron)
points(x = 1875:1972, y = m2_fit, type = 'l', col = 'red')
```

